Cybercrime and Online Video Games

### 2019-12-14 paper/paper.tex
Update paper.tex

\subsection{Sentiment Analysis}
One of our tasks was to analyze the intentions behind each comment, whether
they were criticizing the product or, on the contrary, if they were lauding
the product. For that, we decided to use a Python package provided by scikit-learn.org
We used 3 different machine learning techniques to classify each comment as
either positive or negative: Stochastic Gradient Descent (SGD), Naive Bayes, 
Support Vector machines (SVC). Each algorithm gives each comment a probability to be either positive or negative. We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral.

@@

\subsection{Key Players}
In the context of our project, the key players in the Fortnite hacker forums are those who have the most threads and/or comments under their names. We defined a user as a key player if they posted more than one thread or more than fifty comments from our 104 threads and 7932 comments. We determined these metrics by manually analyzing the comments and threads and determining who were the minority of more active users. These active user threads will usually take the form of either crimeware or CaaS with the poster selling to whoever can pay with some supposedly “legal” methods scattered throughout. Some of the more popular services are account selling, radar hacks, aimbot hacks and cheaper V-Bucks. Below are two pie charts depicting the thread and comment counts with the labels identifying the greater contributors.

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount.png}
	\caption{Thread Count}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount.png}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure}

>>>>

\subsection{Sentiment Analysis}
One of our tasks was to analyze the intentions behind each comment, whether
they were criticizing the product or, on the contrary, if they were lauding
the product. For that, we decided to use a Python package provided by scikit-learn.org
We used 3 different machine learning techniques to classify each comment as
either positive or negative: Stochastic Gradient Descent (SGD), Naive Bayes, 
Support Vector machines (SVC). Each algorithm gives each comment a probability to be either positive or negative. 
We sum each algorithm's score and determine based on that score whether the comment is positive, negative or neutral. Below is a chart
showing the percentage of comments that were deemed positive, negative and neutral.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{SentimentChart.png}
	\caption{Sentiment Analysis Chart}
\end{figure}

@@

\subsection{Key Players}
In the context of our project, the key players in the Fortnite hacker forums are those who have the most threads and/or comments under their names. We defined a user as a key player if they posted more than one thread or more than fifty comments from our 126 threads and 7994 comments. We determined these metrics by manually analyzing the comments and threads and determining who were the minority of more active users. These active user threads will usually take the form of either crimeware or CaaS with the poster selling to whoever can pay with some supposedly “legal” methods scattered throughout. Some of the more popular services are account selling, radar hacks, aimbot hacks and cheaper V-Bucks. Below are two pie charts depicting the thread and comment counts with the labels identifying the greater contributors.

\begin{figure*}[h]
\centering
\begin{subfigure}{.25\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount.png}
	\caption{Thread Count}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount.png}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure*}
